---
title: "Further Analysis"
description: |
  DACSS 603 Final Project Work: "Further Analysis"
preview: education.png
categories:
  - statistics
  - quantitative data analysis
  - final project
  - IT Army of Ukraine
author:
  - name: Kristina Becvar
date: 2022-04-26
output:
  distill::distill_article:
    toc: true
    code_folding: true
    
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plyr); library(dplyr)
library(ggplot2)
library(cowplot)
library(broom)
library(scales)
library(here)
library(magrittr)
```

# Reading in Data

Continuing this post by reading in the data I put together in my exploratory analysis. A full accounting of the variables and descriptions are in the "About" tab of this GitHub Page.

```{r code_folding = TRUE}
#all IVS data
ivs_clean <- read.csv("ivs-df-clean.csv")
ivs_clean <- as_tibble(ivs_clean)
names(ivs_clean)[1] <- 'country'
head(ivs_clean)
```

## Saving other data for potential review

```{r code_folding = TRUE}
ivs_right <- ivs_clean %>%
  group_by(country) %>%
  select(country, right_surveillance, right_monitor, right_collect)
```


```{r code_folding = TRUE}
#integrated data
all_data <- read.csv("integrated_data.csv")
all_data <- as_tibble(all_data)
names(all_data)[1] <- 'country'
head(all_data)
```

# Multiple Linear Regression

## Importance to Respondents

```{r code_folding=TRUE}
#Linear regression of "importance" variables
mlm1 <- lm(users ~ family + friends + leisure + politics + work + religion, data = all_data, na.action = na.exclude)
summary(mlm1)
```

Removing the largest p-value first:

```{r code_folding=TRUE}
#Linear regression of "importance" variables
mlm1b <- lm(users ~ family + friends + politics + work + religion, data = all_data, na.action = na.exclude)
summary(mlm1b)
```

Removing the next largest p-value:

```{r code_folding=TRUE}
#Linear regression of "importance" variables
mlm1c <- lm(users ~ family + friends + politics + work, data = all_data, na.action = na.exclude)
summary(mlm1c)
```

Removing the next largest p-value:

```{r code_folding=TRUE}
#Linear regression of "importance" variables
mlm1d <- lm(users ~ family + politics + work, data = all_data, na.action = na.exclude)
summary(mlm1d)
```

Removing the next largest p-value:

```{r code_folding=TRUE}
#Linear regression of "importance" variables
mlm1e <- lm(users ~ politics + work, data = all_data, na.action = na.exclude)
summary(mlm1e)
```

## Political Inclinations of Respondents

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm2 <- lm(users ~ willingness + petition + boycott + demonstration + strikes + identity, data = all_data, na.action = na.exclude)
summary(mlm2)
```

Removing the highest p-value

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm2b <- lm(users ~ willingness + petition + boycott + demonstration + strikes, data = all_data, na.action = na.exclude)
summary(mlm2b)
```

Removing the next highest p-value

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm2c <- lm(users ~ petition + boycott + demonstration + strikes, data = all_data, na.action = na.exclude)
summary(mlm2c)
```

Removing the next highest p-value

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm2d <- lm(users ~ petition + demonstration + strikes, data = all_data, na.action = na.exclude)
summary(mlm2d)
```

Removing the next highest p-value

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm2e <- lm(users ~ demonstration + strikes, data = all_data, na.action = na.exclude)
summary(mlm2e)
```
Looking at only "demonstration"

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm2f <- lm(users ~ demonstration, data = all_data, na.action = na.exclude)
summary(mlm2f)
```

Plotting this model

```{r code_folding=TRUE}

plot(mlm2f)

```

Looking at only "strikes"

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm2g <- lm(users ~ strikes, data = all_data, na.action = na.exclude)
summary(mlm2g)
```

Plotting the best model

```{r code_folding=TRUE}

plot(mlm2e)

```


## Demographics of Respondents

```{r code_folding=TRUE}
#Linear regression of "demographics" variables
mlm3 <- lm(users ~ marital + parents + children + household + education + income, data = all_data, na.action = na.exclude)
summary(mlm3)
```

Remove highest p-value first

```{r code_folding=TRUE}
#Linear regression of "demographics" variables
mlm3b <- lm(users ~ marital + parents + children + education + income, data = all_data, na.action = na.exclude)
summary(mlm3b)
```

Remove next highest p-value

```{r code_folding=TRUE}
#Linear regression of "demographics" variables
mlm3b <- lm(users ~ marital + parents + education + income, data = all_data, na.action = na.exclude)
summary(mlm3b)
```

Remove next highest p-value

```{r code_folding=TRUE}
#Linear regression of "demographics" variables
mlm3c <- lm(users ~ marital + parents + education, data = all_data, na.action = na.exclude)
summary(mlm3c)
```

Remove next highest p-value

```{r code_folding=TRUE}
#Linear regression of "demographics" variables
mlm3d <- lm(users ~ parents + education, data = all_data, na.action = na.exclude)
summary(mlm3d)
```

## Users to Politics and Education

I'll look at a model that uses combinations of variables from demographics as well as political variables.

```{r code_folding=TRUE}
#Linear regression of "demographics" variables
mlm4 <- lm(users ~  politics + education, data = all_data, na.action = na.exclude)
summary(mlm4)
```

## Users to Strike Propensity and Education

I'll look at a model that uses combinations of variables from demographics as well as political variables.

```{r code_folding=TRUE}
#Linear regression of "demographics" variables
mlm5 <- lm(users ~ strikes + education, data = all_data, na.action = na.exclude)
summary(mlm5)
```

One more combination to try and understand if different variables can create a better model

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm7 <- lm(users ~ demonstration + strikes + education, data = all_data, na.action = na.exclude)
summary(mlm7)
```

```{r code_folding=TRUE}
par(mfrow = c(1,1))
plot(mlm7, 1:6)
```


# Simple Linear Regression

## Potential Correlation with Strike Propensity

I am going to look further at the potential correlation between countries with a propensity to engage in strikes and engage in DDOS attacks.

```{r code_folding=TRUE}
#Linear regression of "politics" variable "strikes"
lm_strikes <- lm(users ~ strikes, data = all_data, na.action = na.exclude)
summary(lm_strikes)
```

## Potential Correlation with Education Level

I am going to look further at the potential correlation between education level with a propensity to engage in strikes and engage in DDOS attacks.

```{r code_folding=TRUE}
#Linear regression of "educational level" and "users"
lm_education <- lm(users ~ education, data = all_data, na.action = na.exclude)
summary(lm_education)
```

It may be that there are no correlations to be found here. But I want to run the analyses again using a column found in the codebook indicating 'weights' for population that should be used when comparing multiple variables to account for population size.

# Adding Population Weights

## Importance to Respondents

I'll re-run the model with users and importance variables, but using the weights column. This gives me a warning that this is an "essentially perfect fit" and that the summary may be reliable. This result is consistent for each of the weighted models.

```{r code_folding=TRUE}
#Linear regression of "importance" variables + weighted   
mlm1w <- lm(users ~ family + friends + leisure + politics + work + religion, data = all_data, na.action = na.exclude, weights)
summary(mlm1w)
```

## Political Inclinations of Respondents

```{r code_folding=TRUE}
#Linear regression of "politics" variables + weighted
mlm2w <- lm(users ~ willingness + petition + boycott + demonstration + strikes + identity, data = all_data, na.action = na.exclude, weights)
summary(mlm2w)
```

## Demographics of Respondents

```{r code_folding=TRUE}
#Linear regression of "demographics" variables + weighted
mlm3w <- lm(users ~ marital + parents + children + household + education + income, data = all_data, na.action = na.exclude, weights)
summary(mlm3w)
```

## The best model I generated with the weights function added

```{r code_folding=TRUE}
#Linear regression of "politics" variables
mlm7b <- lm(users ~ demonstration + strikes + education, data = all_data, na.action = na.exclude, weights)
summary(mlm7b)
```

# Government Right to Access

```{r code_folding=TRUE}
ivs_right <- read.csv("government_rights.csv")
names(ivs_right)[1] <- 'country'
head(ivs_right)
```

## Exploratory Model

```{r code_folding=TRUE}
right <- lm(users ~ surveillance + monitor + collect, data = ivs_right)
summary(right)
```
removing highest p-value

```{r code_folding=TRUE}
right2 <- lm(users ~ surveillance + collect, data = ivs_right)
summary(right2)
```

removing highest p-value

```{r code_folding=TRUE}
right3 <- lm(users ~ collect, data = ivs_right)
summary(right3)
```

