---
title: "Media Data"
description: |
  DACSS 603 Final Project Work: "Media Analysis"
preview: public_interest.png
categories:
  - statistics
  - media analysis
  - quantitative data analysis
  - final project
  - IT Army of Ukraine
author:
  - name: Kristina Becvar
date: 2022-05-04
output:
  distill::distill_article:
    toc: true
    code_folding: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(plyr); library(dplyr)
library(ggplot2)
library(cowplot)
library(broom)
library(scales)
library(here)
require(ggiraph)
require(ggiraphExtra)
```

# Reading in Data

Read in data for both measures of media interest gathered from the Spike/Newswhip media site

Public Interest = Social media interactions on articles

Media Interest = Number of articles published

## Public Interest

```{r code_folding = TRUE}
#public interest
public_interest <- read_csv("IT_Army_ Public_Interest.csv", 
    col_types = cols(Date = col_date(format = "%m/%d/%Y")))
public_interest <- as_tibble(public_interest)
head(public_interest)
```

## Media Interest

```{r code_folding = TRUE}
#media interest
media_interest <- read_csv("IT_Army_ Media_Interest.csv", 
    col_types = cols(Date = col_date(format = "%m/%d/%Y")))
media_interest <- as_tibble(media_interest)
head(media_interest)
```

## Media, Population, and User Data

All measure are in one dataset for analysis.

```{r code_folding = TRUE}
#data frame with all regional observations
regional_all <- read_csv("comprehensive_by_region.csv") 
regional_all <- as_tibble(regional_all)
regional_all
```

### Proportional Data

```{r code_folding = TRUE}
#proportions
proportions <- read.csv("proportions.csv")
proportions
```

### Basic Pearson Correlation

```{r code_folding=TRUE}
cor(regional_all$DDOS_Users, regional_all$Public_Interest, method = "pearson")
```

# Linear Regression

## Simple Correlation of Population and Sample Population

Comparing the population of each region being examined and the representative population of the countries represented in my sample. These are highly correlated.

```{r code_folding=TRUE}
#Linear regression
pop_lm <- lm(Total_Population ~ Sample_Population, data = regional_all, na.action = na.exclude)
summary(pop_lm)
```

## Multiple Linear Correlation of Variables

Explanatory variables are both the public interest and media interest counts with the DDOS user counts as the outcome variable.

```{r code_folding=TRUE}
#Linear regression user and media variables
regional_mlm <- lm(DDOS_Users ~ Public_Interest + Media_Interest, data = regional_all, na.action = na.exclude)
summary(regional_mlm)
```

```{r code_folding=TRUE}
library(stargazer)
stargazer(regional_mlm, type = "text")
```


```{r code_folding=TRUE}
#create plot
regional_plot <- ggplot(regional_all, aes(x = log(Media_Interest), y = log(DDOS_Users), color = Region)) +
   geom_point() +
   geom_smooth(method=lm,se=TRUE,fullrange=TRUE,color="cornflowerblue") +
   labs(title= "Media Interest and Users",
        x= "Media Interest",
        y = "Users") +
    theme_minimal_hgrid()
regional_plot
```


```{r code_folding=TRUE}
#create plot
regional_plot2 <- ggplot(regional_all, aes(x = log(Public_Interest), y = log(DDOS_Users), color = Region)) +
   geom_point() +
   geom_smooth(method=lm,se=TRUE,fullrange=TRUE,color="cornflowerblue") +
   labs(title= "Public Interest and Users",
        x= "Public Interest",
        y = "Users") +
    theme_minimal_hgrid()
regional_plot2
```


### Interaction Term

Fitting another model, this time with an interaction term allowing interaction between population and media interest

```{r code_folding=TRUE}

mlm3d <- lm(DDOS_Users ~ Public_Interest + Media_Interest + Public_Interest*Media_Interest, data = regional_all)

summary(mlm3d)
```

### Single Models

#### Public Interest

```{r code_folding=TRUE}
pi <- lm(DDOS_Users ~ Public_Interest, data = regional_all)
summary(pi)
```

#### Media Interest

```{r code_folding=TRUE}
mi <- lm(DDOS_Users ~ Media_Interest, data = regional_all)
summary(mi)
```

### Multiple Lines

```{r code_folding=TRUE}
gg2 <- ggplot() +
   geom_smooth(aes(log(DDOS_Users), log(Media_Interest)), data = regional_all, fullrange=TRUE,
               method = "lm", se = TRUE, color = "red3") + 
   geom_smooth(aes(log(DDOS_Users), log(Public_Interest)), data = regional_all, fullrange=TRUE,
               method = "lm", se = TRUE, color = "forestgreen") +
  ggtitle("Media Interest and Public Interest & DDOS Users", subtitle = "Green Indicating Public Interest, Red Indicating Media Interest") +
  xlab("log: DDOS Users") +
  ylab("log: Media Interactions") +
  theme_minimal_hgrid()

 gg2 
```


### Stargazer

Fitting the media models with stargazer

```{r code_folding=TRUE}
library(stargazer)
library(tinytex)
library(sandwich)

m1 = lm(DDOS_Users ~ Media_Interest, data = regional_all)
m2 = lm(DDOS_Users ~ Public_Interest, data = regional_all)

model.lst = list(m1, m2)

stargazer(m1,
          m2,
          title="Displaying results for multiple response variables",
          type = "text",
          float = TRUE,
          report = "vcsp",
          se=lapply(model.lst, function(x) sqrt(diag(vcovHC(x, type = "HC1")))),
          no.space = TRUE,
          header=FALSE,
          single.row = TRUE,
          font.size = "small",
          intercept.bottom = F,
          covariate.labels = c("Intercept", "Media Interest", "Public Interest"),
          column.labels = c("Media Interest", "Public Interest"),
          column.separate = c(1, 1),
          digits = 3,
          t.auto = T,
          p.auto = T
          )
```







